Community Embeddings for Facebook Friend Suggestions\\ \thanks{The reported study was partially supported by RFBR grant \textnumero 20-07-00958. The paper was prepared within the framework of the HSE University Project Group Competition 2020-2022.}

### 2020-10-14 paper-ffs.tex
feedback

Algorithm \ref{alg:friend_sug_com} describes in pseudocode how recommendations are computed from ComE BGMM+VI node and community embeddings and community assignments. The advantage of also considers community membership, is that an improvement in time complexity can be obtained, by considering only users in the same community for friend suggestions.

@@

The runtimes for Algorithm \ref{alg:friend_sug} and \ref{alg:friend_sug_com} when considering $K$ as constant or scaling w.r.t the graph $G = (V, E)$ are shown in Table \ref{tab:runtimes}. The number of friend suggestions $N$ is considered constant w.r.t the graph $G = (V, E)$.

@@

When the hyperparameter number of communities $K$ is considered non-constant with respect to the graph $G$, Algorithm \ref{alg:friend_sug_com} reduces the quadratic runtime in comparison to Algorithm \ref{alg:friend_sug_com}.
$K$ can therefore reduce the quadratic summand $\abs{V}^2N$ by only considering users of the same community for friend suggestions. The reduction in time complexity through Algorithm \ref{alg:friend_sug_com} is only scalable when considering $K$ to be scale with the input graph's size. This assumption can be made when considering communities as groups of friends: with ten times more users, these users form ten times more communities.

@@

Fig. \ref{fig:karateclub_spring} shows the 34 nodes and 78 edges of the \textit{Zachary’s Karate Club graph} dataset plotted as a graph with the Python network package networkx's spring layout.\cite{networkx} Spring layout simulates a force-directed representation of the network, by treating edges as springs pulling nodes together and treating nodes as repelling objects, sometimes called an anti-gravity force.\cite{networkx} The node classification, represented by node color, shown in Fig. \ref{fig:karateclub_spring} was obtained by running ComE with BGMM and VI with the hyperparameters presented in Table \ref{tab:params_karateclub}.

@@

As can be seen in Fig. \ref{fig:karateclub_spring}, the two communities in the \textit{Zachary’s Karate Club graph} dataset are correctly identified, despite the number of communities being initialized with $K=5$. Thanks to the Bayesian approach to community modeling and optimization through variational inference, three unused communities are dropped, which leaves the prominent two communities present in the dataset. The node classification obtained reflects the node classification published in the \citeyear{ComE} original ComE paper by \citeauthor{ComE}.\cite{ComE}

@@

The \textit{Social circles: Facebook} dataset was sourced from the profile and network data of ten ego-networks (egonets) through a custom Facebook app by \citeauthor{social_circles_in_ego_networks} as part of their \citeyear{social_circles_in_ego_networks} article \textit{Learning to Discover Social Circles in Ego Networks}.\cite{social_circles_in_ego_networks}

@@

Now that the testing users are identified, the leave-one-out method is employed for obtaining one testing friendship per testing user. The friendship chosen to leave out for testing for each testing user is chosen randomly using NumPy's random choice.\cite{oliphant2006guide, van2011numpy}

@@

Fig. \ref{fig:fb_graphs} shows the graph spring plotted with networkx and nodes colored by community membership after the last iteration of ComE.\cite{networkx} The spring plotted graph structure on Fig. \ref{fig:fb_graphs} suggest, that with embedding dimension $D=4$, more fitting communities are detected than for $D=2$ and $D=128$.

>>>>

Algorithm \ref{alg:friend_sug_com} describes in pseudocode how recommendations are computed from ComE BGMM+VI node and community embeddings and community assignments. The advantage of also considering community membership, is that an improvement in time complexity can be obtained, by considering only users in the same community for friend suggestions.

@@

The runtimes for Algorithm \ref{alg:friend_sug} and \ref{alg:friend_sug_com} when considering $K$ as constant or scaling w.r.t. the graph $G = (V, E)$ are shown in Table \ref{tab:runtimes}. The number of friend suggestions $N$ is considered constant w.r.t. the graph $G = (V, E)$.

@@

When the hyperparameter number of communities $K$ is considered scaling w.r.t. the graph $G$'s size $(\abs{V}, \abs{E})$, Algorithm \ref{alg:friend_sug_com} reduces the quadratic runtime in comparison to Algorithm \ref{alg:friend_sug}.
$K$ can therefore reduce the quadratic summand $\abs{V}^2N$ by only considering users of the same community for friend suggestions. The reduction in time complexity through Algorithm \ref{alg:friend_sug_com} is only scalable when considering $K$ to be scale with the input graph's size. This assumption can be made when considering communities as groups of friends: with ten times more users, these users form ten times more communities.

@@

Fig. \ref{fig:karateclub_spring} shows the 34 nodes and 78 edges of the \textit{Zachary’s Karate Club graph} dataset plotted as a graph with the Python network package networkx's spring layout \cite{networkx}. Spring layout simulates a force-directed representation of the network, by treating edges as springs pulling nodes together and treating nodes as repelling objects, sometimes called an anti-gravity force \cite{networkx}. The node classification, represented by node color, shown in Fig. \ref{fig:karateclub_spring} was obtained by running ComE with BGMM and VI with the hyperparameters presented in Table \ref{tab:params_karateclub}.

@@

As can be seen in Fig. \ref{fig:karateclub_spring}, the two communities in the \textit{Zachary’s Karate Club graph} dataset are correctly identified, despite the number of communities being initialized with $K=5$. Thanks to the Bayesian approach to community modeling and optimization through variational inference, three unused communities are dropped, which leaves the prominent two communities present in the dataset. The node classification obtained reflects the node classification published in the \citeyear{ComE} original ComE paper by \citeauthor{ComE} \cite{ComE}.

@@

The \textit{Social circles: Facebook} dataset was sourced from the profile and network data of ten ego-networks (egonets) through a custom Facebook app by \citeauthor{social_circles_in_ego_networks} as part of their \citeyear{social_circles_in_ego_networks} article \textit{Learning to Discover Social Circles in Ego Networks} \cite{social_circles_in_ego_networks}.

@@

Now that the testing users are identified, the leave-one-out method is employed for obtaining one testing friendship per testing user. The friendship chosen to leave out for testing for each testing user is chosen randomly using NumPy's random choice \cite{oliphant2006guide, van2011numpy}.

@@

Fig. \ref{fig:fb_graphs} shows the graph spring plotted with networkx and nodes colored by community membership after the last iteration of ComE \cite{networkx}. The spring plotted graph structure on Fig. \ref{fig:fb_graphs} suggest, that with embedding dimension $D=4$, more fitting communities are detected than for $D=2$ and $D=128$.
